Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 introduction.tex
Updates from Overleaf

A complexity theoretic reformulation of this problem by Gottesman~\cite{web:Aaronson}

\begin{itemize}
    \item Add some of the very original motivation of delegation (at some philosophical level) to motivate that sampling problem is important and has been sought after from the very beginning. 
    \item quickly survey the topic (Add references and surveys) to Mahadev's results. 
    \item \XW{What're important post-Mahadev's result to discuss here? use subsequentially 3 papers}
\end{itemize}

>>>>

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13} \XW{add more reference})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
\XW{state the Mahadev's result + post Mahadev's development (3 papers)}.
